---
title: 'Report 8: Planned Permanency Caregiver Strengths Attainment'
author: "OACCA - ODP Version 3"
date: ""
header-includes:
- \usepackage{booktabs}
- \usepackage{graphicx}
output:
pdf_document:
fig_height: 3.5
fig_width: 5
keep_tex: yes
html_document:
highlight: espresso
theme: spacelab
---
#Agency `r prog`
```{r, echo=FALSE, warning=FALSE, message=FALSE}
program_name <- gsub("\\d", "", prog) #removes the number in agency
program_name <- substr(program_name, 2, nchar(program_name)) #removes the first character (space)

prog <- df[ df$program_loop == prog, ]
progaggregate <- df[ df$program == program_name, ]

progabove <- prog[prog$age.groups.intake != "0-4 years old", ]
progbelow <- prog[prog$age.groups.intake == "0-4 years old", ]
aboveagg <- progaggregate[progaggregate$age.groups.intake != "0-4 years old", ]
belowagg <- progaggregate[progaggregate$age.groups.intake == "0-4 years old", ]
```

## Children Birth through age 4 
The CANS assessment tools are completed by the agency case manager or social worker for each child at intake and discharge. The CANS Birth - 5 is used for children from birth through age 4.  Each tool contains an Identified Permanent Resource Strengths and Needs subscale.  Caregiver strengths and needs are based on the scores from this subscale.  A lower score indicates a caregiver with more strengths and a higher score indicates a caregiver with more needs.  The tables and figures in Report 8 show only the mean scores of caregivers from any given agency.  Caregiver strengths attainment is measured by lower mean scores at discharge than at intake.

The information contained in this report is based only on those records that meet the criteria for analysis and these are described below:

1. The agency name, program type and program name should be present in the records.
2. Records which indicate the duration of stay is less than or equal to 30 days are not included for analysis.
3. Records should have the Client Demographics and Placement Info submitted to aggregate.
4. Records should have the relevant tool submitted to aggregate and have valid data at both intake and discharge to be included for analysis in those categories.

The tables and figures in the report include only records which contain valid data for associated variables.  The mean scores in the table are averages based on all children who had a completed Identified Permanent Resource Strengths and Needs subscale score.  The scores are displayed for both the individual agency and the aggregate.

The tables show mean differences in CANS Identified Permanent Resource Strengths and Needs subscale category between intake and discharge.  Tables showing N = 0 and % = NA indicate that no data was available to generate information in the table.

###Caregiver Strength Attainment: A Comparison of Scores at Intake and Discharge for Caregivers of Children Ages Birth - 4

\begin{itemize}
\item `r length(belowagg[,1])` Aggregate records available
\item `r length(progbelow[,1])` Agency records available
\end{itemize}

```{r, echo=FALSE, message=FALSE, results='asis', warning=FALSE}

library(xtable)

if(length(belowagg[,1]) > 0){
  cans5b.i = mean(belowagg$r8_total.intake)
  cans5b.d = mean(belowagg$r8_total.discharge)
  nobs = length(belowagg$client_FID)
  
  cans5b.iA = mean(progbelow$r8_total.intake)
  cans5b.dA = mean(progbelow$r8_total.discharge)
  nobsA = length(progbelow$client_FID)
  
  
  tab.1 = cbind.data.frame(nobs, cans5b.i, cans5b.d, nobsA, cans5b.iA, cans5b.dA)
  
  tab.1[is.na(tab.1)] <- "NA"
  
  addtorow <- list()
  addtorow$pos <- list()
  addtorow$pos[[1]] <- 0
  addtorow$pos[[2]] <- 0
  addtorow$command <- c(' \\multicolumn{3}{c}{Aggregate} &  \\multicolumn{3}{c}{Agency} \\\\\n', 'N & Intake & Discharge & N & Intake & Discharge \\\\\n')
  
  print(xtable(tab.1, align="lrrrrrr", caption = "Caregiver Strength Attainment: A Comparison of Scores at \n Intake and Discharge for Caregivers of Children Ages Birth - 4", digits=c(0, 0, 2, 2, 0, 2, 2)), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
  } else{cat("Note: No useable records are available to generate the table and figure.")}
```

```{r, results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.align = "center", fig.path="Graphics/plot"}
if(length(belowagg[,1]) > 0){
  tab.1 = cbind(nobs, cans5b.i, cans5b.d, nobsA, cans5b.iA, cans5b.dA)
  plot(tab.1[, 2:3], type="b", ylim=c(0, 20), ylab="", xaxt="no", xlab="", col="red", main="Figure 1: Caregiver Strength Attainment: A Comparison of Scores at \n Intake and Discharge for Caregivers of Children Ages Birth - 4", cex.axis = 0.8, cex.main = 0.8, font.main = 1, family="serif")
  par(new = T)
  lines(tab.1[,5:6], col = "blue")
  axis(1, at=1:2, labels=c("Intake", "Discharge"), col.axis="black", las=1, cex.axis = .75)
  legend("topright",
         col = c("red", "blue"), pch = c(1, 1), cex = 0.75, legend = c("Aggregate", "Agency"))
}
```


## Children ages 5 and Above 
The CANS assessment tools are completed by the agency case manager or social worker for each child at intake and discharge. The CANS Comprehensive age 5+ is used for children ages 5 and above.  Each tool contains a Planned Permanency Caregiver Strengths and Needs subscale.  Caregiver strengths and needs are based on the scores from this subscale.  A lower score indicates a caregiver with more strengths and a higher score indicates a caregiver with more needs.  The tables and figures in Report 8 show only the mean scores of caregivers from any given agency.  Caregiver strengths attainment is measured by lower mean scores at discharge than at intake.

The information contained in this report is based only on those records that meet the criteria for analysis and these are described below:

1. The agency name, program type and program name should be present in the records.
2. Records which indicate the duration of stay is less than or equal to 30 days are not included for analysis.
3. Records should have the Client Demographics and Placement Info submitted to aggregate.
4. Records should have the relevant tool submitted to aggregate and have valid data at both intake and discharge to be included for analysis in those categories.

The tables and figures in the report include only records which contain valid data for associated variables.  The mean scores in the table are averages based on all children who had a completed Planned Permanency Caregiver Strengths and Needs subscale score.  The scores are displayed for both the individual agency and the aggregate.

The tables show mean differences in CANS Planned Permanency Caregiver Strengths and Needs subscale category between intake and discharge.  Tables showing N = 0 and % = NA indicate that no data was available to generate information in the table.

###Caregiver Strength Attainment: A Comparison of Scores at Intake and Discharge for Caregivers of Children Ages 5+

\begin{itemize}
\item `r length(aboveagg[,1])` Aggregate records available
\item `r length(progabove[,1])` Agency records available
\end{itemize}

```{r, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
if(length(aboveagg[,1]) > 0){
  cans5b.i = mean(aboveagg$r8_total.intake)
  cans5b.d = mean(aboveagg$r8_total.discharge)
  nobs = length(aboveagg$client_FID)
  
  cans5b.iA = mean(progabove$r8_total.intake)
  cans5b.dA = mean(progabove$r8_total.discharge)
  nobsA = length(progabove$client_FID)
  
  
  tab.1 = cbind.data.frame(nobs, cans5b.i, cans5b.d, nobsA, cans5b.iA, cans5b.dA)
  
  tab.1[is.na(tab.1)] <- "NA"
  
  addtorow <- list()
  addtorow$pos <- list()
  addtorow$pos[[1]] <- 0
  addtorow$pos[[2]] <- 0
  addtorow$command <- c(' \\multicolumn{3}{c}{Aggregate} &  \\multicolumn{3}{c}{Agency} \\\\\n', 'N & Intake & Discharge & N & Intake & Discharge \\\\\n')
  

  print(xtable(tab.1, align="lrrrrrr", caption = "Caregiver Strength Attainment: A Comparison of Scores at Intake and Discharge for Caregivers of Children Ages 5+", digits=c(0,0, 2, 2, 0, 2, 2)), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)} else{cat("Note: No useable records are available to generate the table and figure.")}
```


```{r, echo=FALSE, fig.align='center', fig.path= "Graphics/plot"}
if(length(aboveagg[,1]) > 0){
  tab.1 = cbind(nobs, cans5b.i, cans5b.d, nobsA, cans5b.iA, cans5b.dA)
  plot(tab.1[, 2:3], type="b", ylim=c(0, 20), ylab="", xaxt="no", xlab="", col="red", main="Figure 2: Caregiver Strength Attainment: A Comparison of Scores at \n Intake and Discharge for Caregivers of Children Ages 5+", cex.axis = 0.8, cex.main = 0.8, font.main = 1, family="serif")
  par(new = T)
  lines(tab.1[,5:6], col = "blue")
  axis(1, at=1:2, labels=c("Intake", "Discharge"), col.axis="black", las=1, cex.axis = .75)
  legend("topright",
         col = c("red", "blue"), pch = c(1, 1), cex = 0.75, legend = c("Aggregate", "Agency"))
}
```



