---
pdf_document: null
author: "OACCA - ODP Version 3"
date: ""
output: pdf_document
header-includes: \usepackage{booktabs}
highlight: espresso
html_document: null
keep_tex: yes
fig_width: 5
theme: spacelab
fig_height: 3.5
---


# `r prog`
```{r, echo=FALSE, results='hide'}
Total <- sum # Swaps "Total" for "Sum"
prog <- df[ df$program == prog,]
```




## Report 1 -- Demographics

General demographic information is collected on each child entering the program. This report provides the characteristics of those children. The information contained in this report is based only on those records of agencies participating in Version 3. In particular, this report is based on:

\begin{itemize}
  \item `r length(prog$id)` Aggregate records
\end{itemize}



```{r, echo=FALSE, message=FALSE, results='asis'}
library(xtable)

tab.11 = table(prog$age.groups)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind.data.frame(tab.11a[, 2], tab.11c[,2])
row.names(tab.1Main) <- c(levels(prog$age.groups), "Total")

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('Age Group & N & \\% \\\\\n')

print(xtable(tab.1Main, align="lrr", caption = "Age", digits = c(0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=T, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.11 = table(prog$sex)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind.data.frame(tab.11a[, 2], tab.11c[,2])
row.names(tab.1Main) <- c(levels(prog$sex), "Total")

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('Sex & N & \\% \\\\\n')

print(xtable(tab.1Main, align="lrr", caption = "Sex", digits = c(0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=T, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.11 = table(prog$race)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind.data.frame(tab.11a[, 2], tab.11c[,2])
row.names(tab.1Main) <- c(levels(prog$race), "Total")

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('Race & N & \\% \\\\\n')

print(xtable(tab.1Main, align="lrr", caption = "Race", digits = c(0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=T, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.11 = table(prog$diagnosis)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind.data.frame(tab.11a[, 2], tab.11c[,2])
row.names(tab.1Main) <- c(levels(prog$diagnosis), "Total")

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('Diagnosis & N & \\% \\\\\n')

print(xtable(tab.1Main, align="lrr", caption = "Diagnosis", digits = c(0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=T, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.11 = table(prog$los.months)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind.data.frame(tab.11a[, 2], tab.11c[,2])
row.names(tab.1Main) <- c(levels(prog$los.months), "Total")

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('Length of Stay & N & \\% \\\\\n')

print(xtable(tab.1Main, align="lrr", caption = "Length of Stay", digits = c(0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=T, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.11 = table(prog$county.same)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind.data.frame(tab.11a[, 2], tab.11c[,2])
row.names(tab.1Main) <- c(levels(prog$county.same), "Total")

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('Out of County & N & \\% \\\\\n')

print(xtable(tab.1Main, align="lrr", caption = "Out of County", digits = c(0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=T, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.11 = table(prog$nature_discharge)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind.data.frame(tab.11a[, 2], tab.11c[,2])
row.names(tab.1Main) <- c(levels(prog$nature_discharge), "Total")

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('Nature of Discharge & N & \\% \\\\\n')

print(xtable(tab.1Main, align="lrr", caption = "Nature of Discharge", digits = c(0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=T, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```
