---
pnewdf_document: null
author: "OACCA - ODP Version 3"
output: pdf_document
header-includes: \usepackage{booktabs}
highlight: espresso
html_document: null
keep_tex: yes
fig_width: 5
theme: spacelab
fig_height: 3.5
---


# Agency `r prog` %prog is printed as a string to show the agency number and program on the top of the page
```{r, echo=FALSE, results='hide'}
program_name <- gsub("\\d", "", prog) #removes the number in agency
program_name <- substr(program_name, 2, nchar(program_name)) #removes the first character (space)

Total <- sum # Swaps "Total" for "Sum"
prog <- df[ df$program_loop == prog,] #This subsets the data to only those that match prog's agency and program
newdf <- df[ df$program == program_name, ] #Aggregate - this is a subset that matches prog's program to show the aggregate
```




## Report 1 -- Demographics

General demographic information is collected on each child entering the program. This report provides the characteristics of those children. The information contained in this report is based only on those records of agencies participating in Version 3. In particular, this report is based on:

\begin{itemize}
  \item `r length(newdf$id)` Aggregate records
  \item `r length(prog$id)` Agency/Program records
\end{itemize}



```{r, echo=FALSE, message=FALSE, results='asis'}
library(xtable)

tab.1 = table(newdf$age.groups) #Creates a table of the age groups in the aggregate
tab.1a = as.data.frame(addmargins(tab.1, FUN = Total)) #Turns the table into a dataframe and adds the total on the bottom
tab.1b = round(prop.table(tab.1)*100, digits=0) #Table of the age groups' percent porportion
tab.1b2 = prop.table(tab.1)*100
tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total)) #Turns the table into a dataframe and adds the total on the bottom

#The same thing is done to the agency's data
tab.11 = table(prog$age.groups)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind(tab.1a, tab.1c[,2], tab.11a[, 2], tab.11c[,2]) #The agency's data and the aggregate are combined

tab.1Main[is.na(tab.1Main)] <- "NA" #Any missing data is displayed with the "NA" in the table

#The following code is to format the LaTeX code and create a multicolumn for Agency and Aggregate and to name all the columns explicitly
addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$pos[[2]] <- 0
addtorow$command <- c('& \\multicolumn{2}{c}{Aggregate} &  \\multicolumn{2}{c}{Agency} \\\\\n', 'Age Group & N & \\% & N & \\% \\\\\n')

print(xtable(tab.1Main, align="llrrrr", caption = "Age", digits=c(0, 0, 0, 2, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.1 = table(newdf$sex)
tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
tab.1b = round(prop.table(tab.1)*100, digits=0)
tab.1b2 = prop.table(tab.1)*100
tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total))

tab.11 = table(prog$sex)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind(tab.1a, tab.1c[,2], tab.11a[, 2], tab.11c[,2])

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$pos[[2]] <- 0
addtorow$command <- c('& \\multicolumn{2}{c}{Aggregate} &  \\multicolumn{2}{c}{Agency} \\\\\n', 'Sex & N & \\% & N & \\% \\\\\n')

print(xtable(tab.1Main, align="llrrrr", caption = "Sex", digits=c(0, 0, 0, 2, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.1 = table(newdf$race)
tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
tab.1b = round(prop.table(tab.1)*100, digits=0)
tab.1b2 = prop.table(tab.1)*100
tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total))

tab.11 = table(prog$race)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind(tab.1a, tab.1c[,2], tab.11a[, 2], tab.11c[,2])

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$pos[[2]] <- 0
addtorow$command <- c('& \\multicolumn{2}{c}{Aggregate} &  \\multicolumn{2}{c}{Agency} \\\\\n', 'Race & N & \\% & N & \\% \\\\\n')

print(xtable(tab.1Main, align="llrrrr", caption = "Race", digits=c(0, 0, 0, 2, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.1 = table(newdf$diagnosis)
tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
tab.1b = round(prop.table(tab.1)*100, digits=0)
tab.1b2 = prop.table(tab.1)*100
tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total))

tab.11 = table(prog$diagnosis)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind(tab.1a, tab.1c[,2], tab.11a[, 2], tab.11c[,2])

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$pos[[2]] <- 0
addtorow$command <- c('& \\multicolumn{2}{c}{Aggregate} &  \\multicolumn{2}{c}{Agency} \\\\\n', 'Diagnosis & N & \\% & N & \\% \\\\\n')

print(xtable(tab.1Main, align="llrrrr", caption = "Diagnosis", digits=c(0, 0, 0, 2, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.1 = table(newdf$los.months)
tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
tab.1b = round(prop.table(tab.1)*100, digits=0)
tab.1b2 = prop.table(tab.1)*100
tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total))

tab.11 = table(prog$los.months)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind(tab.1a, tab.1c[,2], tab.11a[, 2], tab.11c[,2])

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$pos[[2]] <- 0
addtorow$command <- c('& \\multicolumn{2}{c}{Aggregate} &  \\multicolumn{2}{c}{Agency} \\\\\n', 'Length of Stay & N & \\% & N & \\% \\\\\n')

print(xtable(tab.1Main, align="llrrrr", caption = "Length of Stay", digits=c(0, 0, 0, 2, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.1 = table(newdf$county.same)
tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
tab.1b = round(prop.table(tab.1)*100, digits=0)
tab.1b2 = prop.table(tab.1)*100
tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total))

tab.11 = table(prog$county.same)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind(tab.1a, tab.1c[,2], tab.11a[, 2], tab.11c[,2])

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$pos[[2]] <- 0
addtorow$command <- c('& \\multicolumn{2}{c}{Aggregate} &  \\multicolumn{2}{c}{Agency} \\\\\n', 'Out of county? & N & \\% & N & \\% \\\\\n')

print(xtable(tab.1Main, align="llrrrr", caption = "Out of County", digits=c(0, 0, 0, 2, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, message=FALSE, results='asis'}
tab.1 = table(newdf$nature_discharge)
tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
tab.1b = round(prop.table(tab.1)*100, digits=0)
tab.1b2 = prop.table(tab.1)*100
tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total))

tab.11 = table(prog$nature_discharge)
tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
tab.11b = round(prop.table(tab.11)*100, digits=0)
tab.11b2 = prop.table(tab.11)*100
tab.11c = as.data.frame(addmargins(tab.11b2, FUN = Total))

tab.1Main = cbind(tab.1a, tab.1c[,2], tab.11a[, 2], tab.11c[,2])

tab.1Main[is.na(tab.1Main)] <- "NA"

addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$pos[[2]] <- 0
addtorow$command <- c('& \\multicolumn{2}{c}{Aggregate} &  \\multicolumn{2}{c}{Agency} \\\\\n', 'Nature of Discharge & N & \\% & N & \\% \\\\\n')

print(xtable(tab.1Main, align="llrrrr", caption = "Nature of Discharge", digits=c(0, 0, 0, 2, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```
