---
title: 'Report 4: Restrictiveness of Living Environment'
author: "OACCA - ODP Version 3"
date: ""
header-includes:
  - \usepackage{booktabs}
  - \usepackage{graphicx}
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 5
    keep_tex: yes
  html_document:
    highlight: espresso
    theme: spacelab
---

# `r prog`

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
progaggregate <- df[ df$program.intake == prog, ]
```

The Restrictiveness of Living Environments Scale (ROLES) is used to track the following data points:

1. where a child was living just prior to intake (pre-placement),
2. where a child was living during placement (placement),
3. where a child was being discharged to after placement (discharge), and,
4. where a child had been living in the six months after discharge (post-placement).

A score was given at each of these points in time based on the weights given to the environments listed on the ROLES by Hawkins et al. (1992), where the most restrictive setting is jail (10.0) and the least restrictive setting is independent living by self (0.5).
The information contained in this report is based only on those records that meet the criteria for analysis and these are described below:

1. The agency name, program type and program name should be present in the records.
2. Records which indicate the duration of stay is less than or equal to 30 days are not included for analysis.
3. Records should have the Client Demographics and Placement Info submitted to aggregate.
4. Records should have a valid response to living environment after discharge in Discharge Summary as well as ROLES completed at intake and discharge to be included for analysis for Table 1 and Figure 1.
5. Records should have Follow-up Summary submitted to aggregate and the number of days entered for different living environments at follow-up should equal 180.  Additionally records should have a ROLES completed at intake and discharge as well as records outlined in number 4 above to be included in Figure 2 and Table 2 in this report which shows the mean - or average - ROLES score for each of the four points in time, based on the weights given to ROLES. These are based only on those cases in which all four data points were provided.

Figure 1 and Table 1 display changes in restrictiveness of living between three points in time - 90 days prior to placement, during placement, and the living environment to which the child is being discharged.

Figure 2 and Table 2 display changes in restrictiveness of living between the discharge and follow-up, as these two points specifically address the goal that a child will progress to a less restrictive living environment at the conclusion of placement and will maintain or improve to an even less restrictive environment post-discharge.  As stated above, a lower ROLES score indicates a less restrictive living environment.

If data was missing at discharge or follow-up, those children were placed in the "unknown" category, as restrictiveness of living changes between discharge and post-placement (follow-up) could not be determined. This category includes cases where the agency was unable to contact the family/child at follow-up. Each table in the report includes only records which contain valid data for the associated variables.

The tables and figures provide numbers and percentages for analysis and comparison. Tables showing N = 0 and % = NA indicate that no data was available to generate information in the table.

###Restrictiveness of Living Levels Prior to Placement, During Placement and to which the Child will be discharged

\begin{itemize}
  \item `r length(progaggregate$client_FID)` Aggregate records available
\end{itemize}


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(xtable)

roles.pp = mean(progaggregate$p2a_total.intake, na.rm = T)
roles.p = mean(progaggregate$p2a_total.discharge, na.rm = T)
roles.d = mean(progaggregate$home.discharge, na.rm = T)
nobs = length(progaggregate$client_FID)
  
tab.1 = cbind(nobs, roles.pp, roles.p, roles.d)
  
addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('N & Prior to Placement & During Placement & Discharge \\\\\n')
  
print(xtable(tab.1, align="lrrrr", caption = "Restrictiveness of Living Levels Prior to Placement, During Placement and to which the Child will be discharged", digits=c(0, 0, 2, 2, 2)), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, fig.align='center', fig.path= "Figure/plots"}

  plot(tab.1[, 2:4], type="b", ylim=c(0, 20), ylab="", xaxt="no", xlab="", col="red", main="Figure 1: Restrictiveness of Living Levels", cex.main=0.8, cex.axis = .8, font.main = 1, family="serif", las=1)
  par(new = T)
  axis(1, at=1:3, labels=c("Prior to Placement", "During Placement", "Discharge"), col.axis="black", cex.lab = 0.75, las=1, cex.axis = .75)
```

###Restrictiveness of Living Levels at Discharge and at Follow-up

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
 progaggregate <- subset(progaggregate, !is.na(p2atotal_followup))
```

\begin{itemize}
  \item `r length(progaggregate$client_FID)` Aggregate records available
\end{itemize}



```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
  if(mean(progaggregate$p2atotal_followup, na.rm = T) != "NaN"){
roles.d = mean(progaggregate$home.discharge, na.rm = T)
roles.f = mean(progaggregate$p2atotal_followup, na.rm = T)  
nobs = length(progaggregate$client_FID)
  
tab.2 = cbind(nobs, roles.d, roles.f)
  
addtorow <- list()
addtorow$pos <- list()
addtorow$pos[[1]] <- 0
addtorow$command <- c('N & Discharge & Follow-up \\\\\n')
  
print(xtable(tab.2, align="lrrr", caption = "Restrictiveness of Living Levels at Discharge and at Follow-up", digits=c(0, 0, 2, 2)), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
  } else{cat("Note: No useable records are available to generate the table and figure.")}
```


```{r, echo=FALSE, fig.align='center', fig.path= "Figure/plots"}
  if(mean(progaggregate$p2atotal_followup, na.rm = T) != "NaN"){
plot(tab.2[, 2:3], type="b", ylim=c(0, 20), ylab="", xaxt="no", xlab="", col="red", main="Figure 2: Restrictiveness of Living Levels", cex.main=0.8, cex.axis = .8, font.main = 1, family="serif", las=1)
par(new = T)
axis(1, at=1:2, labels=c("Discharge", "Follow-up"), col.axis="black", cex.lab = 0.75, las=1, cex.axis = .75)
}
```
