---
title: 'Report 7: Transition to Independence for Children ages 17+'
author: "OACCA - ODP Version 3"
date: ""
header-includes:
   - \usepackage{booktabs}
   - \usepackage{graphicx}
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 5
    keep_tex: yes
  html_document:
    highlight: espresso
    theme: spacelab
---
#Agency `r prog`
```{r, echo=FALSE, warning=FALSE, message=FALSE}
program_name <- gsub("\\d", "", prog) #removes the number in agency
program_name <- substr(program_name, 2, nchar(program_name)) #removes the first character (space)

Total <- sum
prog <- df[ df$program_loop == prog, ]
progaggregate <- df[ df$program == program_name, ]
```

Youth who are 17 years or older are assessed for employment outcomes in relationship to some education outcomes six months after being discharged from a placement.  Information on these variables is obtained at follow-up by the agency.

The information contained in this report is based only on those records that meet the criteria for analysis and these are described below:

1. The agency name, program type and program name should be present in the records.
2. Records which indicate the duration of stay is less than or equal to 30 days are not included for analysis.
3. Records should have the Client Demographics, Placement Info and Follow-up Summary submitted to aggregate.

Each table in the report includes only records which contain valid data for associated variables. The table shows the percentage of children ages 17+ in each of the seven categories.  Tables showing N = 0 and % = NA indicate that no data was available to generate information in the table.

###Employment for Youth 17 and Older by Percentage

\begin{itemize}
\item `r length(progaggregate[,1])` Aggregate records available
\item `r length(prog[,1])` Agency records available
\end{itemize}

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

# Table 1: Employment for Youth 17 and Older by Percentage (percentage,*** number, agency and aggregate*)
library(xtable)
  tab.1 = table(progaggregate$ind_final)
  tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
  tab.1b = prop.table(tab.1)*100
  tab.1c = as.data.frame(addmargins(tab.1b, FUN = Total))
  
  tab.11 = table(prog$ind_final)
  tab.11a = as.data.frame(addmargins(tab.11, FUN = Total))
  tab.11b = prop.table(tab.11)*100
  tab.11c = as.data.frame(addmargins(tab.11b, FUN = Total))
  
  tab.1Main = cbind(tab.1a, tab.1c[,2], tab.11a[, 2], tab.11c[,2])
  
  addtorow <- list()
  addtorow$pos <- list()
  addtorow$pos[[1]] <- 0
  addtorow$pos[[2]] <- 0
  addtorow$command <- c('& \\multicolumn{2}{c}{Aggregate} &  \\multicolumn{2}{c}{Agency} \\\\\n', 'Employment & N & \\% & N & \\% \\\\\n')
  
  print(xtable(tab.1Main, align="llrrrr", caption = "Employment for Youth 17 and Older by Percentage", digits=c(0, 0, 0, 2, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
```


```{r, echo=FALSE, fig.align='center', fig.path="Figures/plots"}
# Figure 1: Employment for Youth 17 and Older by Percentage (bar graph**** showing percent of youth in each category for agency and aggregate*)
    tab.1plot = cbind(as.matrix(tab.1b), as.matrix(tab.11b))
  colnames(tab.1plot) <- c("Aggregate", "Agency")
  names.arg = c("Attending School/\nSeeking a GED",
  "Diploma/GED\nand Employed...",
  "Diploma/GED\nand Attending...",
  "Dropped out/\nExpelled and...",
  "Diploma/GED\nand no employment...",
  "Dropped out/Expelled\nand no employment...",
  "Unknown")
op <- par(mar = c(11,2,2,2) + 0.1)
barplot(tab.1plot, ylim=c(0, 100), beside = TRUE, ylab="Percent", col="gray", main="Figure 1: Employment for Youth 17 and Older by Percentage", xlab = "", xaxt="no", cex.main=0.9, las = 2, cex.axis = 0.8, cex.names = 0.8, font.main = 1, family="serif")
axis(1, at = c(1.5:7.5, 9.5:15.5), labels = c(names.arg, names.arg), cex.axis = 0.55, las=2)
text(4.5, 75, cex = 0.8, pos = 3, "Aggregate")
text(12.5, 75, cex = 0.8, pos = 3, "Agency")
par(op)
```

