---
title: 'Report 10: Safety'
author: "OACCA - ODP Version 3"
date: ""
header-includes:
- \usepackage{booktabs}
- \usepackage{graphicx}
output:
pdf_document:
fig_height: 3.5
fig_width: 5
keep_tex: yes
html_document:
highlight: espresso
theme: spacelab
---

# `r prog`

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
Total <- sum
agglength <- df[ df$program == prog, ]
```


It is expected that children placed in substitute care will be sheltered from abuse and/or neglect.  Nevertheless at times abuse/neglect may occur while the child is in care.  The Discharge Summary collects data on whether the child was a victim of indicated or substantiated abuse and/or neglect while in care.  

The information contained in this report is based only on those records that meet the criteria for analysis and these are described below:

1. The agency name, program type and program name should be present in the records.
2. Records should have the Client Demographics and Placement Info submitted to aggregate.

The table and figure in this report provides basic frequencies (percentages) for each of the response options for the question related to safety.  Table 1 and Figure 1 contain only those records where the Discharge Summary has been submitted to aggregate and specifically determine whether the outcome goal was achieved. A "no" response indicates that a child was not been a victim of indicated or substantiated abuse and/or neglect while in the placement.

###Safety During Placement

\begin{itemize}
\item `r length(agglength$program)` Aggregate records available
\end{itemize}



```{r, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
library(xtable)

if(length(agglength$client_FID) > 0){
  tab.1 = table(agglength$abuse)
  tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
  tab.1b = round(prop.table(tab.1)*100, digits=0)
  tab.1b2 = prop.table(tab.1)*100
  tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total))
  
  tab.1Main = cbind(tab.1a, tab.1c[,2])
  
  addtorow <- list()
  addtorow$pos <- list()
  addtorow$pos[[1]] <- 0
  addtorow$command <- c('Abuse/Neglect & N & \\% \\\\\n')
  
  print(xtable(tab.1Main, align="llrr", caption = "Abuse/Neglect", digits = c(0, 0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)} else{cat("Note: No useable records are available to generate the table and figure.")}
```


```{r, echo=FALSE, results='hide', fig.align='center', fig.path="Figures/plot"}
if(length(agglength$client_FID) > 0){
  barplot(tab.1b, ylim=c(0, 100), beside = TRUE, ylab="Percent", xlab="Abuse/Neglect", col="gray", main="Figure 1: Safety During Placement", cex.main=0.8, cex.axis = .8, font.main = 1, family="serif")
}
```

Additionally outcome goals include that children will remain free of indicated or substantiated abuse and/or neglect post discharge. At Follow-Up, data is collected on whether the child had any indicated or substantiated abuse and/or neglect since leaving the program. 

The information contained in this report is based only on those records that meet the criteria for analysis and these are described below:

1. The agency name, program type and program name should be present in the records.
2. Records which indicate the duration of stay is less than or equal to 30 days are not included for analysis.
3. Records should have the Client Demographics and Placement Info submitted to aggregate.

The table and figure in this report provides basic frequencies (percentages) for each of the response options for the question related to safety.  Table 2 and Figure 2 contain only those records where the Follow-up Summary has been submitted to aggregate and specifically determine whether the outcome goal was achieved. A "no" response indicates that a child has not been a victim of indicated or substantiated abuse and/or neglect since leaving the placement.

### Safety Post Discharge

```{r, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
agglength <- df2[ df2$program == prog, ]
agglength <- agglength[!is.na(agglength$abuse),]
```

\begin{itemize}
\item `r length(agglength$program)` Aggregate records available
\end{itemize}

```{r, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
if(length(agglength$program) > 0){
  tab.1 = table(agglength$abuse)
  tab.1a = as.data.frame(addmargins(tab.1, FUN = Total))
  tab.1b = round(prop.table(tab.1)*100, digits=0)
  tab.1b2 = prop.table(tab.1)*100
  tab.1c = as.data.frame(addmargins(tab.1b2, FUN = Total))
  
  tab.1Main = cbind(tab.1a, tab.1c[,2])
  #colnames(tab.1Main) =c("Age", "Aggregate (N)", "Aggregate (%)", "Agency (N)", "Agency (%)")
  
  addtorow <- list()
  addtorow$pos <- list()
  addtorow$pos[[1]] <- 0
  addtorow$command <- c('Abuse/Neglect & N & \\% \\\\\n')
  
  print(xtable(tab.1Main, align="llrr", caption = "Safety Post Discharge", digits = c(0, 0, 0, 2)),hline.after = c(0, -1, (length(tab.1Main[,1])-1), length(tab.1Main[,1])), type='latex', comment=FALSE, include.rownames=FALSE, include.colnames = F, caption.placement = "top", booktabs = TRUE, add.to.row = addtorow)
  } else{cat("Note: No useable records are available to generate the table and figure.")}
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.align='center', fig.path="Figures/plot"}
if(length(agglength$program) > 0){
  barplot(tab.1b, ylim=c(0, 100), beside = TRUE, ylab="Percent", xlab="Abuse/Neglect", col="gray", main="Figure 2: Safety Post Discharge", cex.main=0.8, cex.axis = .8, font.main = 1, family="serif")
}
```
